Gammapy: A Python package for gamma-ray astronomy

### 2023-03-03 src/ms-review.tex
Fix #118
Fix #121

To handle the spatial dimension the sub-package exposes a uniform API for
the FITS World Coordinate System (WCS), the HEALPix pixelization and
region-based data structure (see Figure~\ref{fig*:minted:gp_maps}).
This allows uses to perform the same higher level operations on maps
independent of the underlying pixelisation scheme.

@@

The \code{Fit} class provides a uniform interface to multiple fitting backends:
\begin{itemize}
	\setlength\itemsep{1em}
	\item \iminuit~\citep{iminuit}
	\item \code{scipy.optimize}~\citep{2020SciPy-NMeth}
	\item \sherpa~\citep{sherpa-2011}
\end{itemize}

>>>>

To handle the spatial dimension the sub-package exposes a uniform API for
the FITS World Coordinate System (WCS), the HEALPix pixelization and
region-based data structure (see Figure~\ref{fig*:minted:gp_maps}).
This allows users to perform the same higher level operations on maps
independent of the underlying pixelisation scheme. The \code{gammapy.maps}
package is also used by external packages such as \textit{FermiPy}~\citep{Wood2017}

@@

The \code{Fit} class provides a uniform interface to multiple fitting backends:
\begin{itemize}
	\setlength\itemsep{1em}
	\item \iminuit~\citep{iminuit}
	\item \code{scipy.optimize}~\citep{2020SciPy-NMeth}
	\item \sherpa~\citep{sherpa-2011, sherpa-2001}
\end{itemize}
